Tomographic galaxy clustering with the Subaru Hyper Suprime-Cam first year public data release

### 2019-11-18 doc/Paper/main.tex
responses

  \subsection{Survey mask}\label{ssec:methods.mask}
    \begin{figure}
      \centering
      \includegraphics[width=0.49\textwidth]{figures/mask_GAMA09H.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_GAMA15H.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_HECTOMAP.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_VVDS.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_WIDE12H.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_XMMLSS.pdf}
      \caption{Sky masks for the 6 fields used in this analysis. The map pixels contain values between 0 and 1, corresponding to the fraction of the pixel's area not covered by the fiducial bright-object mask.}
      \label{fig:masks}
    \end{figure}
    The reconstruction of the survey geometry is a central step in order to obtain unbiased estimates of the angular power spectrum. This information is encoded in the so-called ``survey mask'', which minimally contains binary information about which areas of the sky should (mask $=1$) or should not (mask $=0$) be used in the analysis. The basis for our survey mask is the so-called ``bright-object mask'' \cite{2018PASJ...70S...7C}, provided with the HSC DR1, which flags sources that are close to bright stars (mag $<17.5$), with a magnitude-dependent exclusion radius (see \cite{2018PASJ...70S...7C} for details). It is worth noting that the information about the bright object mask is encoded in the HSC DR1 at the catalog level in terms of per-object flags. We transform this information into a pixelized sky map through a multi-step process:
    \begin{enumerate}
      \item We start by creating a low-resolution binary mask based on the presence of objects from the raw catalog in a given pixel. This mask has a pixel size of 0.6 arcmin. The large number density of the raw catalog  ($n_g\sim30\,{\rm arcmin}^{-2}$) is high enough that masked pixels are unlikely to correspond to intrinsically empty regions of the sky, but rather completely unobserved pixels.
      \item We upgrade the low-resolution binary mask to a higher resolution (0.2 arcmin), and remove all pixels containing objects flagged by the bright object mask. We then remove all disconnected, unmasked groups of pixels, corresponding to spurious islands within the exclusion radius of a bright object with no sources in the catalogs.
      \item We downgrade the resulting mask back to the original resolution through an averaging procedure, producing a map quantifying the observed fraction of each pixel.
    \end{enumerate}
    It is worth noting that the resolution of the resulting mask ($0.6$ arcminutes) defines the resolution of all maps used in this analysis. After this procedure, we further mask all pixels with a $10\sigma$ depth below our magnitude limit of $i<24.5$, where the depth is estimated as described in Section \ref{ssec:methods.syst}.

@@

  \subsubsection{Halo Occupation Distribution}\label{sssec:methods.theory.hod}
    In order to model $P_{gg}(z,k)$ we use a halo occupation distribution (HOD) model \citep{2000MNRAS.318.1144P,2002PhR...372....1C,2002ApJ...575..587B,2005ApJ...633..791Z,2013MNRAS.430..725V}. In this halo model-based prescription we model the galaxy content of dark matter haloes as a function of halo mass. Details about HOD parameterizations can be found in \cite{2011ApJ...736...59Z}. In short, the galaxy power spectrum receives contributions from the so-called 1-halo and 2-halo terms:
    \begin{equation}
      P_{gg}(z,k) = P_{gg,{\rm 1h}}(z,k) + P_{gg,{\rm 2h}}(z,k),
    \end{equation}
    where
    \begin{align}
      & P_{gg,{\rm 1h}}(k)=\frac{1}{\bar{n}_g^2} \int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M} \bar{N}_c\,\left[\bar{N}_s^2u_s^2(k)+2\bar{N}_su_s^2(k)\right],\\
      & P_{gg,{\rm 2h}}(k)=\left(\frac{1}{\bar{n}_g} \int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M}\,b_h(M)\,\bar{N}_c\,\left[1+\bar{N}_su_s(k)\right]\right)^2\,P_{\rm lin}(k).
    \end{align}
    Here, $M$ represents halo mass, $\sfrac{\mathrm{d}n}{\mathrm{d}M}$ is the halo mass function, $b_h(M)$ is the halo bias, $\bar{N}_c(M)$ and $\bar{N}_s(M)$ are the mean number of central and satellite galaxies respectively, $u_s(k)$ is the Fourier transform of the normalized density profile of satellite galaxies, $P_{\rm lin}(k)$ is the linear matter power spectrum and $\bar{n}_g$ is the total mean galaxy density, given by
    \begin{equation}
      \bar{n}_g=\int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M}\bar{N}_c(M)\left[1+\bar{N}_s(M)\right].
      \label{eq:ng_hod}
    \end{equation}
    A central assumption in standard HOD parameterizations is that centrals/satellites follow a Bernoulli/Poisson distribution.

@@

    In the presence of magnification, the equations presented in Section \ref{ssec:methods.theory} acquire additional terms. The projected galaxy overdensity becomes:
    \begin{equation}
      \delta^i_g(\nv)=\int \mathrm{d}z\,\left[p^i(z)\,\Delta_g+\frac{W_\mu^i(z)}{H(z)}\nabla_\theta^2\nabla^{-2}\Delta_m\right],
    \end{equation}
    where $\Delta_m$ is the 3D matter overdensity (we have omitted the dependence on $t$ and $\chi\nv$ for brevity) and $W_\mu$ is the magnification kernel
    \begin{equation}
      W_\mu(z)=\frac{3H_0^2\Omega_{m}(1+z)}{2}\int_z^\infty \mathrm{d}z'\,p^i(z)\,\left(5s(z')-2\right)\,\frac{\chi(z')-\chi(z)}{\chi(z)\chi(z')}.
    \end{equation}
    Here, $H_0\equiv H(z=0)$, $\Omega_{m}$ is the fractional matter density today, and $s$ is the logarithmic slope of the cumulative apparent magnitude distribution $N(<m, z)$:
    \begin{equation}
      \left. s(z) \equiv \frac{\partial \log_{10}N(<m, z)}{\partial m}\right \rvert_{m=m_{\mathrm{lim}}},
      \label{eq:s-func}
    \end{equation}
    where $m$ denotes the observed magnitude and $m_{\mathrm{lim}}$ is the magnitude limit of the galaxy sample considered. In short, the observed density contrast does not depend solely on the distribution of galaxies in the tomographic redshift bin of interest, but also on the distribution of matter along the line of sight to these galaxies. Overdensities along the line of sight cause the local angular separation between galaxies to increase (lowering the observed number density), while lensing magnification causes fainter galaxies to enter the observed sample (increasing the observed number density). The two effects cancel at leading order when $s=\sfrac{2}{5}$.

>>>>

  \subsection{Survey mask}\label{ssec:methods.mask}
    \begin{figure}
      \centering
      \includegraphics[width=0.49\textwidth]{figures/mask_GAMA09H.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_GAMA15H.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_HECTOMAP.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_VVDS.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_WIDE12H.pdf}
      \includegraphics[width=0.49\textwidth]{figures/mask_XMMLSS.pdf}
      \caption{Sky masks for the 6 fields used in this analysis. The map pixels contain values between 0 and 1, corresponding to the fraction of the pixel's area not covered by the fiducial bright-object mask.}
      \label{fig:masks}
    \end{figure}
    The reconstruction of the survey geometry is a central step in order to obtain unbiased estimates of the angular power spectrum. This information is encoded in the so-called ``survey mask'', which minimally contains binary information about which areas of the sky should (mask $=1$) or should not (mask $=0$) be used in the analysis. The basis for our survey mask is the so-called ``bright-object mask'' \cite{2018PASJ...70S...7C}, provided with the HSC DR1, which flags sources that are close to bright stars (mag $<17.5$), with a magnitude-dependent exclusion radius (see \cite{2018PASJ...70S...7C} for details). It is worth noting that the information about the bright object mask is encoded in the HSC DR1 at the catalog level in terms of per-object flags. We transform this information into a pixelized sky map through a multi-step process:
    \begin{enumerate}
      \item We start by creating a low-resolution binary mask based on the presence of objects from the raw catalog in a given pixel. This mask has a pixel size of 0.6 arcmin. The large number density of the raw catalog  ($n_g\sim30\,{\rm arcmin}^{-2}$) is high enough that masked pixels are unlikely to correspond to intrinsically empty regions of the sky, but rather completely unobserved pixels.
      \item We upgrade the low-resolution binary mask to a higher resolution (0.2 arcmin), and remove all pixels containing objects flagged by the bright object mask. We then remove all disconnected, unmasked groups of pixels, corresponding to spurious islands within the exclusion radius of a bright object with no sources in the catalogs.
      \item We downgrade the resulting mask back to the original resolution through an averaging procedure, producing a map quantifying the observed fraction of each pixel.
    \end{enumerate}
    We verified that the resulting mask is robust by comparing the power spectra estimated with it with those found with an observed fraction map defined simply as the fraction of objects in each pixel outside the bright object mask. It is worth noting that the resolution of this mask ($0.6$ arcminutes) defines the resolution of all maps used in this analysis. After this procedure, we further mask all pixels with a $10\sigma$ depth below our magnitude limit of $i<24.5$, where the depth is estimated as described in Section \ref{ssec:methods.syst}.

@@

  \subsubsection{Halo Occupation Distribution}\label{sssec:methods.theory.hod}
    In order to model $P_{gg}(z,k)$ we use a halo occupation distribution (HOD) model \citep{2000MNRAS.318.1144P,2002PhR...372....1C,2002ApJ...575..587B,2005ApJ...633..791Z,2013MNRAS.430..725V}. In this halo model-based prescription we model the galaxy content of dark matter haloes as a function of halo mass. Details about HOD parameterizations can be found in \cite{2011ApJ...736...59Z}. In short, the galaxy power spectrum receives contributions from the so-called 1-halo and 2-halo terms:
    \begin{equation}
      P_{gg}(z,k) = P_{gg,{\rm 1h}}(z,k) + P_{gg,{\rm 2h}}(z,k),
    \end{equation}
    where
    \begin{align}
      & P_{gg,{\rm 1h}}(k)=\frac{1}{\bar{n}_g^2} \int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M} \bar{N}_c\,\left[\bar{N}_s^2u_s^2(k)+2\bar{N}_su_s^2(k)\right],\\
      & P_{gg,{\rm 2h}}(k)=\left(\frac{1}{\bar{n}_g} \int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M}\,b_h(M)\,\bar{N}_c\,\left[1+\bar{N}_su_s(k)\right]\right)^2\,P_{\rm lin}(k).
    \end{align}
    Here, $M$ represents halo mass, $\sfrac{\mathrm{d}n}{\mathrm{d}M}$ is the halo mass function, $b_h(M)$ is the halo bias, $\bar{N}_c(M)$ and $\bar{N}_s(M)$ are the mean number of central and satellite galaxies respectively, $u_s(k)$ is the Fourier transform of the normalized density profile of satellite galaxies, $P_{\rm lin}(k)$ is the linear matter power spectrum and $\bar{n}_g$ is the total mean galaxy density, given by
    \begin{equation}
      \bar{n}_g=\int \mathrm{d}M\,\frac{\mathrm{d}n}{\mathrm{d}M}\bar{N}_c(M)\left[1+\bar{N}_s(M)\right].
      \label{eq:ng_hod}
    \end{equation}
    A central assumption in standard HOD parameterizations is that centrals/satellites follow a Bernoulli/Poisson distribution. The model used here also assumes that halos can only contain satellites if they contain a central.

@@

    In the presence of magnification, the equations presented in Section \ref{ssec:methods.theory} acquire additional terms. The projected galaxy overdensity becomes:
    \begin{equation}
      \delta^i_g(\nv)=\int \mathrm{d}z\,\left[p^i(z)\,\Delta_g+\frac{W_\mu^i(z)}{H(z)}\nabla_\theta^2\nabla^{-2}\Delta_m\right],
    \end{equation}
    where $\Delta_m$ is the 3D matter overdensity (we have omitted the dependence on $t$ and $\chi\nv$ for brevity) and $W_\mu$ is the magnification kernel
    \begin{equation}
      W_\mu(z)=\frac{3H_0^2\Omega_{m}(1+z)}{2}\int_z^\infty \mathrm{d}z'\,p^i(z)\,\left(5s(z',m_{\rm lim})-2\right)\,\frac{\chi(z')-\chi(z)}{\chi(z)\chi(z')}.
    \end{equation}
    Here, $H_0\equiv H(z=0)$, $\Omega_{m}$ is the fractional matter density today, and $s$ is the logarithmic slope of the cumulative apparent magnitude distribution $N(<m, z)$:
    \begin{equation}
      \left. s(z,m_{\rm lim}) \equiv \frac{\partial \log_{10}N(<m, z)}{\partial m}\right \rvert_{m=m_{\mathrm{lim}}},
      \label{eq:s-func}
    \end{equation}
    where $m$ denotes the observed magnitude and $m_{\mathrm{lim}}$ is the magnitude limit of the galaxy sample considered. In what follows we will omit the dependence of $s$ on $m_{\rm lim}$ for brevity. In short, the observed density contrast does not depend solely on the distribution of galaxies in the tomographic redshift bin of interest, but also on the distribution of matter along the line of sight to these galaxies. Overdensities along the line of sight cause the local angular separation between galaxies to increase (lowering the observed number density), while lensing magnification causes fainter galaxies to enter the observed sample (increasing the observed number density). The two effects cancel at leading order when $s=\sfrac{2}{5}$.
